---
title: "Lab 00 - Hello IDS!"
author: "Hamish Lothian"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Hamish", "Herman", "Rudy", 
           "Matt", "Abdul"),
  github_username = c("hamlot12", "hermansokr", "rudyadair", "matthurrell", "7aman4013"), 
  colour = c("purple", "yellow", "green", 
             "red", "blue"),
  hobby = c("Golf", "Drawing", "Cricket", 
            "Badminton", "Coding"),
  favourite_number = c(9, 4, 3, 6, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


It shows a bar chart displaying the favourite number of each person with their username under their bar. The bars are also filled by the person's favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite Number",
          title = "Team Numbers")
```

The labs command changes the chart title and labels.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The graph does not display the data well as there is little to no change in the height of the graph and across a larger scale of data the graph would be far too wide to read. An alternative would be to display the hobbys as a table with the peoples names next to their hobby. This table would be sorted alphabetically by hobby.
